Multi agents systems and comlexity that goes along can be a source of a great excitement. It is remarkable how a system
comprising a set of agent with very limited capabilities to reasoning and decision making produces outstandingly good
solutions to very difficult problems. From global economy to simulated ant colonies, small agents applying their best
judgement and acting in their own best interst get things done, sometimes as gracefully as no well organized and
well-financed think tank on the entire Earth could ever do. It has been known for quite a long time that a beautiful
whirl of a seemingly chaotic swarm of mostly independent agents can make solutions emerge.

Have we had solutions just appear by themselves, this world would not be half as spectacular. Need for problems to be
solved and absense of low-hanging answers to our problems stimulate us to form structures and impose objectives on them,
and as for multi agent ones we have two ways to go. The first is to set agents up and let things happen. As appealing as
it is and as
%TODO: "as it can be": ant colonies, ANNs
effective as it can be, this approach does not always deliver the outcomes we want. The second one is to create a rigid
system of absolute control. When creating a PID controller for a thermostat, this is exactly what we want. But for
bigger systems, this approach may fall due to lack of flexibility, and in systems involving people, it
does so with dire consequences.

The advantage of the option in between those two extremes is arguably the flexibility it has. We can roughly delineate
two aspects in the process of that flexible group decision making: strategic and tactic. The first one is all about
so-called "big picture". Some entity that is entitled to establish the direction of the group's strategy, given that it
has all the necessary information, can reason in bigger-scale terms and define the general course of action for the
entire group. However, it cannot (and should not) oversee all the details of the strategy's particular implementation
instances. It is better to delegate this part of decision making to smaller groups or individual agents. There is no
one-size-fits-all solutions in systems comprising multiple entities, and some are better made in an ad-hoc manner.
% TODO: "some" what?
Situational awareness of individual agents may and often does possesses very valuable information that sure should be
considered before a decision is made.

The question is how do we reconcile the necessity to adhere to the global strategy, and yet at the same time do not make
the system so rigid so individual agents become unable to apply the best of their situational awareness to make the best
solution possible within the confinements of the general strategy that is defined. How do we translate our general
objectives into individual agents' decision making processes?

It would be a far-fetched statement to say that we know the answer to that in terms of practically applicable group
control. But we believe that we have to offer a mechanism for simulating group control that possesses some of the
aforementioned properties such as flexibility and separation of strategic and tactical decision making while having them
both within the same process. Most likely, the approach is not yet practically applicable in its current form, but we
hope that further development of the idea will make practical results come to fruition.

The approach to simulating group control that we mentioned is based on using a weighted graph of preference hierarchy
higher levels of which "map" to strategic objectives, while lower levels do so to tactical ones. Nodes of the graph
which we call "aspects" are interpreted as parts of the general objective; edges' weights connecting aspects represent
preference of child aspects within the \textit{context} of the parent aspect.

% TODO: justify the novelty. We are not the first ones offering to tweak parts of the graph. Use the IMMOD article, it
% offers a good explaination of why our work is valuable.

The aim of this research is to prototype the idea that has been formulated in our previous work.
% TODO: reference to the work
Since it is written in
russian, we duplicate some parts of it describing the mechanism in order to give you the entire picture.

%TODO: references
The work follows the following structure. First, we explain the idea and offer an algorithm implementing it. We created
a simulation based on the algorithm to have a proof of concept, so the next part is devoted to the details regarding how
the simulation is implemented. And then we give a brief overview of the simulation's results, draw some conclusions, and
offer ways of its further development.

We open-sourced the source code for the simulation \cite{github}. You are encouraged to examine, fork, modify, and use
it in your projects as you see fit.
